Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-01-24 DryDep.tex
Finished acknowledgments.

Although dry deposition to ice and snow amounts to less than $1\,\unit{\%}$ of the total global annual ozone dry deposition, a decrease in prescribed dry deposition velocity in accordance to combined measurements and model studies \citep{ACP:Helmig2007} causes almost a doubling in the surface ozone concentrations in the high Arctics and affects surface ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. By comparing with results from the multi-model evaluation \citep{ACP:Hardacre2015}, we conclude that it is important to use this updated ozone dry deposition velocity to counter an Arctic surface ozone low-bias in the model, however, this could lead to an overcompansation (high-bias).

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (268073).\\
  %We would like to thank Greg Bodeker, Stefanie Kremser (Bodeker Scientific) and Birgit Hassler (DLR) for providing the combined vertical ozone profile database (\url{http://www.bodekerscientific.com}.
  The used Leaf Area Index (LAI) and roughness length ($z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
  Randerson, J.T., G.R. van der Werf, L. Giglio, G.J. Collatz, and P.S. Kasibhatla. 2018. Global Fire Emissions Database, Version 4, (GFEDv4). ORNL DAAC, Oak Ridge, Tennessee, USA. https://doi.org/10.3334/ORNLDAAC/1293
  We would like to thank Prof. Frode Stordal (Section for Meteorology and Oceanography, University of Oslo) for discussions regarding early drafts of the manuscript as well as Anne Fouilloux (scientific programmer at the same institut) for technical support.
\end{acknowledgements}

>>>>

Although dry deposition to ice and snow amounts to less than $1\,\unit{\%}$ of the total global annual ozone dry deposition, a decrease in prescribed dry deposition velocity in accordance to combined measurements and model studies \citep{ACP:Helmig2007} causes almost a doubling in the surface ozone concentrations in the high Arctics and affects surface ozone concentrations down to latitudes at about $50\,\unit{^\circ}$ in both hemispheres. By comparing with results from the multi-model evaluation \citep{ACP:Hardacre2015}, we conclude that it is important to use this updated ozone dry deposition velocity to counter an Arctic surface ozone low-bias in the model, however, this could lead to an overcompensation (high-bias).

@@

\begin{acknowledgements}
  This work was supported by the Norwegian Research Council (NRC) through the project The double punch: Ozone and climate stresses on vegetation (268073).\\
  The simulations were performed on resources provided by UNINETT Sigma2 -- the National Infrastructure for High Performance Computing and Data Storage in Norway (project nn2806k).\\
  The used Leaf Area Index (LAI) and roughness length ($z_0$) are available online from Oak Ridge National Laboratory Distributed Active Archive Center, Oak Ridge, Tennessee, U.S.A. (\doi{10.3334/ORNLDAAC/970}).\\
  Community Emission Data System (CEDS) historical emission inventory is provided by the Joint Global Research Institute project (\url{http://www.globalchange.umd.edu/ceds/}.)
  Randerson, J.T., G.R. van der Werf, L. Giglio, G.J. Collatz, and P.S. Kasibhatla. 2018. Global Fire Emissions Database, Version 4, (GFEDv4). ORNL DAAC, Oak Ridge, Tennessee, USA. https://doi.org/10.3334/ORNLDAAC/1293
  We would like to thank Prof. Frode Stordal (Section for Meteorology and Oceanography, University of Oslo) for discussions regarding early drafts of the manuscript as well as Anne Fouilloux (scientific programmer at the same institute) for technical support.
  We would also like to thank the Center for International Climate Research (CICERO) for their support of this work.
\end{acknowledgements}
